Approximation as Differentiation notes

### 2025-04-10 main.tex
Update class file; rename main LaTeX file.
Authors.
Move notes to appendix.

\documentclass[acmsmall,nonacm]{acmart}

@@

\title{Approximation as Differentiation notes}
\maketitle

\section{Overview}

Covered so far:
\begin{itemize}
\item $\CMon$-enriched categories, including enriched functors and enriched Yoneda embedding (\secref{cmon-enriched})
\item biproducts and semi-additive categories (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction $\Grothendieck{C}F$ and category of families $\Fam(C)$ (\secref{grothendieck})
\item Examples of useful semi-additive categories (\secref{useful-semi-additive-categories}):
   \begin{itemize}
   \item category $\LatGal$ of bounded lattices and Galois connections (\secref{categories-with-biproducts:latgal})
   \item category $\FinVect_F$ of finite-dimensional vector spaces over a field $F$
   (\secref{categories-with-biproducts:fdvect})
   \end{itemize}
\end{itemize}

\noindent $\Set$ will usually be $\Setoid$ in the Agda implementation but we will gloss that detail for now.

\input{notes/sec/notation}

\section{Definitions}

\input{notes/sec/cmon-enriched}
\input{notes/sec/biproduct}
\input{notes/sec/fam}
\input{notes/sec/set-indexed-product}
\input{notes/sec/grothendieck}
\input{notes/sec/useful-semi-additive-categories}

% \input{notes/language}

\section{Some references}

\cite{karvonen2020}

>>>>

\documentclass[acmsmall,screen]{acmart}

@@

\title{Approximation as Differentiation notes}

\author{Robert Atkey}
\email{robert.atkey@strath.ac.uk}
\orcid{0000-0002-4414-5047}
\affiliation{%
  \institution{University of Strathclyde}
  \city{Glasgow}
  \country{UK}}

\author{Roly Perera}
\email{roly.perera@cl.cam.ac.uk}
\orcid{0000-0001-9249-9862}
\affiliation{%
  \institution{University of Cambridge}
  \city{Cambridge}
  \country{UK}
}
\additionalaffiliation{%
   \institution{University of Bristol}
   \city{Bristol}
   \country{UK}
}

\begin{abstract}
[Abstract]
\end{abstract}
\maketitle

\input{main/introduction}

\pagebreak
\appendix
\input{appendix/notes}
